---
title: "Instruction to R Downloading, Customizing and Updating(Windows)"
author: "Chenhui Hao"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=FALSE)

```
R is a free software environment for statistical computing and graphics. Here is a simple instruction for windows users to download, customize and update R.

## 1. Installing R
You can check the following link if you install R for the first time. Also, you can find further details about the latest version of R and the FAQs here!

[**Current Windows Version of R**](https://cran.r-project.org/){target="_blank"}

You can also install the current windows version R-3.6.1(81 megabytes, 32/64 bit)by the following link. When installing R, you may just accept the default settings.

[**Download R 3.6.1 for Windows**](https://cran.r-project.org/bin/windows/base/R-3.6.1-win.exe){target="_blank"}

## 2. Customizing R
After downlading the new version of R, you may want to customize some settings. Here are the things you might want to change.
###  2.1. Change the R enviroment
When R starts up, it will read the **.RProfile** belonging to the individual user if it exists. you can modify this file to customize your particular R environment.

We will focus on two important potential functions. If .RProfile contains a function called **.First**, this function will be executed first. Similarly, the function named **.Last** will be executed at the end of an R session. Here is an example. 

```{r}
.First <- function(){
 # options(repos=structure(c(CRAN=""))
 cat("\nWelcome at", date(), "\n") 
}
# the .Last() function can be used to save the workspace image to a consistent directory,

# regardless of the current working directory
.Last <- function(){ 
 cat("\nGoodbye at ", date(), "\n")
}
```
You might want to change other things, here is the website where you can find further details.

[**Customizing Startup**](https://www.statmethods.net/interface/customizing.html){target="_blank"}

## 3. Updating R
Here are some tips for packages after you install a new version of R.
The new version of R is installed in a new directory. Therefore, one of the common problems is that you may need to reinstall all of the packages.

###   3.1. Find out the packages and install them manually
You may have trouble remembering all the names of your packages in the old version. In order to find out them and install them in to new one, you can follow this strategy.

#### 3.11. Identify the packages installed in the old version of R

By the following command, you can identify all the packages that you installed and the ones come with R.
```{r}
installed.packages()
```
You can choose the columns you want to see by typing this, for example the 1st and 4th columns(the package name and priority) 
```{r}
installed.packages()[,c(1,4)]
```
If you want to see the first 4 columns, you can type this
```{r}
installed.packages()[,1:4]
```
####  3.12. Install the packages into new version of R

In order to install packages to your new version of R, you can choose the **Packages** from the **Pulldown Menu**, and then click **Install Packages from CRAN**. You can look for the packages name that you want to install and select more than one package at one time by pressing the **control key** and **left click**.

###  3.2. Find out the directory of packages and install them at once
Your new version of R does not have as many packages as your previous version of R, you can just copy the library derictory from the old version of R to the new one by the following steps.

####  3.21. Identify the libarary directory on the previous and new version of R.

To see where your packages are stored, you can use the following command in both of your old and new version of R.
```{r}
.Library
```

####  3.22. Copy the library directory from the old version of R to the new one.
You can then use windows explorer to copy the library directory from your old version of R to your new version R.

####  3.23. Update the packages
Some of the packages in your previous version of R may be out of date. If you want to update those packages, you just need to use this command 
```{r}
update.packages()
```
You can also use the option ask=F if you do not want to be asked about every package updating, as shown below.
```{r}
update.packages(ask=F)
```
